---
title: "On the dynamics of mark-ups, results section"
author: "Curtis Kephart and David Munro"
output:
  pdf_document:
    toc: yes
    toc_depth: 2
    fig_height: 4
    fig_width: 7
  html_notebook:
    toc: yes
    toc_depth: 2
  html_document:
    toc: yes
    toc_depth: 2
---

```{r, echo=FALSE, error=FALSE,  message=FALSE, warning=FALSE, cache=FALSE, include=FALSE}
library(dplyr)
library(ggplot2)
library(knitr)
library(tidyr)
library(memisc)

source("etl.r")

```

# Summary Statistics

Summary of sessions and subjects.

```{r, message = FALSE, warning = FALSE, echo = FALSE, error=FALSE,  cache=FALSE}


sessDat %>%
  group_by(group_size_str) %>%
  summarise(
    Sessions = session.code %>% unique %>% length,
    Subjects = participant.code %>% unique %>% length,
    Periods  = player.period_number %>% unique %>% length 
  ) %>%
  kable(
    format = "markdown",
    align = c("l","c","c","c"),
    col.names = c("Number of Players", "Sessions", "Subjects", "Periods")
  )

```


Sessions were run at the New York University Abu Dhabi and the United Arab Emerates with undergraduate students between Oct 17 and Oct 19th, 2017. 

Subjects earned on average \$`r -30 + (SsPay %>% filter(!(Payment %in% c(0,30))))$Payment %>% mean %>% round(2)` from the experiment. After a 30 AED show-up fee and rounding up to the 5 AED, subjects walked away on average with \$`r (SsPay %>% filter(!(Payment %in% c(0,30))))$Payment %>% mean %>% round(2)`

The experiment was conducted with oTree (*Citation: Chen, D.L., Schonger, M., Wickens, C., 2016. oTree - An open-source platform for laboratory, online and field experiments. Journal of Behavioral and Experimental Finance, vol 9: 88-97*) subjects were recruited with hroot (*Citation: Bock, Olaf, Ingmar Baetge & Andreas Nicklisch (2014). hroot – Hamburg registration and organization online tool. European Economic Review 71, 117-120*)


# Hypothesis 1 - competitiveness and mark-ups

**Hypothesis 1**. *Static mark-ups will be lower in more competitive (higher N) markets.*

```{r, message = FALSE, warning = FALSE, echo = FALSE, error=FALSE,  cache=FALSE}
avg_per_prices <- function(
  data = sessDat,
  rp = NULL
){
  df = sessDat %>%
  filter(
    !is.na(period_half)
    & player.rp == rp
  )

df2 = df %>%
  group_by(group_size_str, player.transport_cost, player.period_number, participant.code,period_half, player.mc) %>%
  dplyr::summarise(
    Price = mean(player.price),
    Price_Median = median(player.price),
    price_se_Up1 = Price + se(player.price),
    price_se_Dwn1 = Price - se(player.price)
  )

p1 = df %>%
  ggplot(
  ) +
  facet_grid(group_size_str ~ period_half) +
  geom_violin(
    aes(y = player.price,
        x = player.transport_cost,
        group = player.transport_cost),
    alpha = 0.3,
    color = "grey70"
  ) +
  geom_ribbon(
    data = df2 %>% 
      group_by(group_size_str, player.transport_cost, player.mc, period_half) %>%
      summarise(
        mean_price = mean(Price),
        price_se_Up1 = mean_price + se(Price),
        price_se_Dwn1 = mean_price - se(Price)
      ), 
    aes(
      x = player.transport_cost,
      ymax = price_se_Up1,
      ymin = price_se_Dwn1,
      group = player.mc,
      fill = player.mc
      
    ),
    alpha = .2
  ) +
  geom_line(
    data = df2 %>% 
      group_by(group_size_str, player.transport_cost, player.mc, period_half) %>%
      summarise(
        mean_price = mean(Price)
      )  , 
    aes(
      x = player.transport_cost,
      y = mean_price,
      group = player.mc,
      color = player.mc
    )
  ) +
  geom_jitter(
    aes(
      y = Price,
      x = player.transport_cost
    ),
    
    data = df2,
    width = 0.02,
    height = 0,
    alpha = 0.2) + 
  scale_x_continuous(
    breaks = c(0.1, 0.25, 0.4, 0.6)
  ) +
  theme_bw() +
  labs(
    x = "Shopping Cost",
    y = "Price",
    title = glue("Average Period Prices, RP: {rp}")
  )

return(p1)
  
}

avg_per_prices(rp = 1.0)
avg_per_prices(rp = 0.9)
avg_per_prices(rp = 0.8)



```

In the pilot we had a spread of transport costs from 0.1 to 1.0. Between 0.1 and 0.5 there wasn't a huge difference in price, only at 0.75 and 1.0 did we see a substantial increase in markups. In this design we only had a spread of transport costs between 0.1 and 0.6, and we don't see a consistent increase in price as transport costs increase. 
I'm sorry I didn't catch that.


```{r, message = FALSE, warning = FALSE, echo = FALSE, error=FALSE,  cache=FALSE}

df = bind_rows(
  sesDat2p %>% 
    dplyr::filter(player.transport_cost != 0.25) %>%
    mutate(playerNum = "Two Players"),
  sesDat4p %>% 
    mutate(playerNum = "Four Players")
)

df2 = df %>%
  group_by(playerNum, player.transport_cost, player.period_number, participant.code) %>%
  dplyr::summarise(
    Price = mean(player.price),
    Price_Median = median(player.price),
    price_se_Up1 = Price + se(player.price),
    price_se_Dwn1 = Price - se(player.price)
  )



ggplot(
  df2
) +
  facet_grid(playerNum ~ .) +
  geom_violin(
    aes(y = Price,
        x = player.transport_cost,
        group = player.transport_cost),
    alpha = 0.3,
    color = "grey70"
  ) +
  geom_ribbon(
    data = df2 %>% 
      group_by(playerNum, player.transport_cost) %>%
      summarise(
        mean_price = mean(Price),
        price_se_Up1 = mean_price + se(Price),
        price_se_Dwn1 = mean_price - se(Price)
      ), 
    aes(
      x = player.transport_cost,
      ymax = price_se_Up1,
      ymin = price_se_Dwn1
    ),
    alpha = .2
  ) +
  geom_line(
    data = df2 %>% 
      group_by(playerNum, player.transport_cost) %>%
      summarise(
        mean_price = mean(Price)
      )  , 
    aes(
      x = player.transport_cost,
      y = mean_price
    )
  ) +
  geom_jitter(
    aes(
      y = Price,
      x = player.transport_cost
    ),
    
    data = df2,
    width = 0.02,
    height = 0,
    alpha = 0.3) + 
  scale_x_continuous(
    breaks = c(0.1, 0.25, 0.5, 0.75, 1.0)
  ) +
  theme_bw() +
  labs(
    x = "Shopping Cost",
    y = "Price",
    title = "Average Period Prices"
  )





  
```

In the plot above, 

- each dot is the average price per subject in one period (20 subperiods) with fixed shopping costs and player count. 
- violins are similarly based on average player-period prices. 
- the line is the average price for that player-number, shopping cost comvination, 
- ribben is the confidence interval. 
- A very similar plot appears when looking at all prices over all subperiods. 



Comparing prices in both treatments. 

```{r, message = FALSE, warning = FALSE, echo = FALSE, error=FALSE,  cache=FALSE}

df = bind_rows(
  sesDat2p %>% 
    dplyr::filter(player.transport_cost != 0.25) %>%
    mutate(playerNum = "Two Players"),
  sesDat4p %>% 
    mutate(playerNum = "Four Players")
)


df2 = df %>%  
  group_by(playerNum, player.transport_cost, participant.code, player.period_number) %>%
  dplyr::summarise(
    player.price = mean(player.price)
  ) %>%
  group_by(playerNum, player.transport_cost) %>%
  dplyr::summarise(
    Price = paste(mean(player.price) %>% round(2), " (±", se(player.price) %>% round(4),  ")", sep="")
  )

kable(
  format = "markdown",
  df2 %>%tidyr::spread(
    player.transport_cost, Price
  ),
  align = c("l","c","c","c","c","c"),
  col.names = c("", "s = 0.1","s = 0.25","s = 0.5","s = 0.75","s = 1"),
  caption = "adsfse"
)

```

Now, looking just at the later half of each period, subperiods 11 to 20, (remove from final)

```{r, message = FALSE, warning = FALSE, echo = FALSE, error=FALSE,  cache=FALSE}


df2 = df %>% 
  dplyr::filter(
    subsession.round_number > 10
  ) %>%
  group_by(playerNum, player.transport_cost, participant.code, player.period_number) %>%
  dplyr::summarise(
    player.price = mean(player.price)
  ) %>%
  group_by(playerNum, player.transport_cost) %>%
  dplyr::summarise(
    Price = paste(mean(player.price) %>% round(2), " (±", se(player.price) %>% round(4),  ")", sep="")
  )

kable(
  format = "markdown",
  df2 %>%tidyr::spread(
    player.transport_cost, Price
  ),
  align = c("l","c","c","c","c","c"),
  col.names = c("", "t = 0.1","t = 0.25","t = 0.5","t = 0.75","t = 1"),
  caption = "adsfse"
)

```


Strong evidence for Hypothesis 1. 

- Looking at the average prices within a period (all 20 subperiods) with the same player number and transport cost, there is a statistically significant difference between prices at each transport level between player number treatments. 
- Even comparing `t = 1.0` in the four player game -- the transport cost in which the four-player game had the highest prices --
to `t = 0.1` in the two player game -- in which prices were the lowest in the two-player game -- the two player game has statistically significantly higher prices (p-value < 0.001). 


```{r, message = FALSE, warning = FALSE, echo = FALSE, error=FALSE,  cache=FALSE}
df = bind_rows(
  sesDat2p %>% 
    dplyr::filter(player.transport_cost != 0.25) %>%
    mutate(playerNum = "Two Players"),
  sesDat4p %>% 
    mutate(playerNum = "Four Players")
)


df2 = df %>%  
  group_by(playerNum, player.transport_cost, participant.code, player.period_number) %>%
  dplyr::summarise(
    player.price = mean(player.price)
  )



with(df2, 
     t.test(player.price[(playerNum == "Two Players" & player.transport_cost == 0.1)],player.price[(playerNum == "Four Players" & player.transport_cost == 1)]
     )
)
with(df2, 
     wilcox.test(player.price[(playerNum == "Two Players" & player.transport_cost == 0.1)], 
            player.price[(playerNum == "Four Players" & player.transport_cost == 1.0)]
     )
)


```

# Hypothesis 2 - shipping costs and mark-ups

**Hypothesis 2** - *There is a positive relationship between shopping costs and mark-ups.*

```{r, message = FALSE, warning = FALSE, echo = FALSE, error=FALSE,  cache=FALSE}
# two player
df = bind_rows(
  sesDat2p %>% 
    dplyr::filter(player.transport_cost != 0.25) %>%
    mutate(playerNum = "Two Players"),
  sesDat4p %>% 
    mutate(playerNum = "Four Players")
)

df2 = df %>%
    dplyr::filter(playerNum == "Two Players")%>%
  group_by(playerNum, player.transport_cost, player.period_number, participant.code) %>%
  dplyr::summarise(
    Price = mean(player.price),
    Price_Median = median(player.price),
    price_se_Up1 = Price + se(player.price),
    price_se_Dwn1 = Price - se(player.price)
  )

p1 = ggplot(
  df2
) +
  geom_violin(
    aes(y = Price,
        x = player.transport_cost,
        group = player.transport_cost),
    alpha = 0.3,
    color = "grey70"
  ) +
  geom_ribbon(
    data = df2 %>% 
      group_by(playerNum, player.transport_cost) %>%
      summarise(
        mean_price = mean(Price),
        price_se_Up1 = mean_price + se(Price),
        price_se_Dwn1 = mean_price - se(Price)
      ), 
    aes(
      x = player.transport_cost,
      ymax = price_se_Up1,
      ymin = price_se_Dwn1
    ),
    alpha = .2
  ) +
  geom_line(
    data = df2 %>% 
      group_by(playerNum, player.transport_cost) %>%
      summarise(
        mean_price = mean(Price)
      )  , 
    aes(
      x = player.transport_cost,
      y = mean_price
    )
  ) +
  geom_jitter(
    aes(
      y = Price,
      x = player.transport_cost
    ),
    
    data = df2,
    width = 0.02,
    height = 0,
    alpha = 0.3) + 
  scale_x_continuous(
    breaks = c(0.1, 0.25, 0.5, 0.75, 1.0)
  ) +
  theme_bw() +
  labs(
    x = "Shopping Cost",
    y = "Price",
    title = "Average Period Prices - Two Players"
  ) +
  coord_cartesian(xlim = c(0,1.1), ylim = c(0,1)) 
p1
```

```{r, message = FALSE, warning = FALSE, echo = FALSE, error=FALSE,  cache=FALSE}
# Four player
df = bind_rows(
  sesDat2p %>% 
    dplyr::filter(player.transport_cost != 0.25) %>%
    mutate(playerNum = "Two Players"),
  sesDat4p %>% 
    mutate(playerNum = "Four Players")
)

df2 = df %>%
    dplyr::filter(playerNum == "Four Players")%>%
  group_by(playerNum, player.transport_cost, player.period_number, participant.code) %>%
  dplyr::summarise(
    Price = mean(player.price),
    Price_Median = median(player.price),
    price_se_Up1 = Price + se(player.price),
    price_se_Dwn1 = Price - se(player.price)
  )



p2 = ggplot(
  df2
) +
  geom_violin(
    aes(y = Price,
        x = player.transport_cost,
        group = player.transport_cost),
    alpha = 0.3,
    color = "grey70"
  ) +
  geom_ribbon(
    data = df2 %>% 
      group_by(playerNum, player.transport_cost) %>%
      summarise(
        mean_price = mean(Price),
        price_se_Up1 = mean_price + se(Price),
        price_se_Dwn1 = mean_price - se(Price)
      ), 
    aes(
      x = player.transport_cost,
      ymax = price_se_Up1,
      ymin = price_se_Dwn1
    ),
    alpha = .2
  ) +
  geom_line(
    data = df2 %>% 
      group_by(playerNum, player.transport_cost) %>%
      summarise(
        mean_price = mean(Price)
      )  , 
    aes(
      x = player.transport_cost,
      y = mean_price
    )
  ) +
  geom_jitter(
    aes(
      y = Price,
      x = player.transport_cost
    ),
    
    data = df2,
    width = 0.02,
    height = 0,
    alpha = 0.3) + 
  scale_x_continuous(
    breaks = c(0.1, 0.25, 0.5, 0.75, 1.0)
  ) +
  theme_bw() +
  labs(
    x = "Shopping Cost",
    y = "Price",
    title = "Average Period Prices - Four Players"
  ) +
  coord_cartesian(xlim = c(0,1.1), ylim = c(0,1)) 
p1
p2

```



```{r, echo = F, eval = T, tidy = T}

df = bind_rows(
  sesDat2p %>% 
    dplyr::filter(player.transport_cost != 0.25) %>%
    mutate(playerNum = "Two Players"),
  sesDat4p %>% 
    mutate(playerNum = "Four Players")
)

df = df %>%
  group_by(playerNum, player.transport_cost, player.period_number, participant.code) %>%
  dplyr::summarise(
    Price = mean(player.price)
  )

df = df %>%
  ungroup() %>%
  group_by(playerNum, player.transport_cost) %>%
  summarise(
    n=n(),
    mean_price = mean(Price) %>% round(3),  
    median_price = median(Price) %>% round(3),
    se_price = (sd(Price)/(n)^0.5)  %>% round(3)
  ) 

kable(
  format = "markdown", 
  df,  align = c("c"),
  col.names = c("","Shopping Cost","N","Mean Price","Median Price","Standard Error")
)
```



- `n` that's each subject was exposed to 3 treatments of each shopping cost level. The two-player game had 16 subjects and the four-player had 24. 

## Initial Look at Two-Player Game

First, within the two player game, comparing prices in `t = 0.1` and `t = 1.0` (see below), there is to be a statistically significant difference. 

There is a relationship between prices and shopping cost treatments. In higher shopping cost settings subjects tended to have higher prices. 

- Unit of observation is an individual's average price within a period, at a set shopping cost level. 
- A t test comparing prices between min and max shopping costs. Prices are average price at the session, participant, and period level. P-value 0.000029.
- A MW rank sum test comparing prices between min and max shopping costs. Prices are average price at the session, participant, and period level. P-value 0.0002061.

```{r, echo=FALSE}
df =  sesDat2p %>%
  ungroup() %>%
  group_by(session.code, participant.code, player.transport_cost,player.period_number) %>%
   summarise(
     mean_price = mean(player.price)
   )
with(df, t.test(mean_price[player.transport_cost == 0.1], mean_price[player.transport_cost == 1.0]))
with(df, wilcox.test(mean_price[player.transport_cost == 0.1], mean_price[player.transport_cost == 1.0]))

```



## Initial Look at Four-Player Game

In the four-player game the relationship, at least between the lowest and highest shopping cost, appears stronger. 

- A t test comparing prices between min and max shopping costs. Prices are average price at the session, participant, and period level. P-value 0.00000023.
- A MW rank sum test comparing prices between min and max shopping costs. Prices are average price at the session, participant, and period level. P-value < 0.000001


```{r, echo=FALSE}
df =  sesDat4p %>%
  ungroup() %>%
  group_by(session.code, participant.code, player.transport_cost,player.period_number) %>%
   summarise(
     mean_price = mean(player.price)
   )
with(df, t.test(mean_price[player.transport_cost == 0.1], mean_price[player.transport_cost == 1.0]))
with(df, wilcox.test(mean_price[player.transport_cost == 0.1], mean_price[player.transport_cost == 1.0]))

```


## Model

```{r, message = FALSE, warning = FALSE, echo = FALSE, error=FALSE, cache=FALSE}

df =  sesDat2p %>%
  dplyr::filter(
    player.transport_cost != 0.25
  ) %>%
  ungroup() %>%
  group_by(session.code, participant.code, player.transport_cost,player.period_number) %>%
  mutate(
    player.round_payoff = player.round_payoff * max(subsession.round_number) #deal with f'ing t=0.25...
  ) %>%
  summarise(
    price = mean(player.price),
    median_price = median(player.price),
    twoPlayer = 1,
    playerNum = "Two Players"
  )

df = bind_rows(
  df, 
  sesDat4p %>%
    ungroup() %>%
    group_by(session.code, participant.code, player.transport_cost,player.period_number) %>%
    mutate(
      player.round_payoff = player.round_payoff * max(subsession.round_number) #deal with f'ing t=0.25...
    ) %>%
    summarise(
      price = mean(player.price),
      median_price = median(player.price),
      twoPlayer = 0,
      playerNum = "Four Players"
    )
) %>%
  ungroup() %>%
  dplyr::mutate(
    stdz_price = (mean(price) - price) / sd(price)
  )

p1= ggplot(
  df,
  aes(
    x = player.transport_cost,
    y = price,
    group = playerNum,
    color = playerNum
  )
) +
  geom_jitter(
    aes(y = log(price)),
    width = 0.07,
    alpha = .4) +
  geom_smooth(
    formula = log(y) ~ log(x)
  ) +
  theme_bw() +
  labs(
    x = "Shopping Cost",
    y = "Log Price"
    
  )
p1
```

Here we have a log-log model regressing prices on shopping costs, with player-number fixed effects. 

$ln(P_{ip}) = \beta_0 + \beta_1 \delta_{i} +\beta_2 ln(S_{ip}) + \beta_3 Period_p + \epsilon_{(ip)}$

```{r, message = FALSE, warning = FALSE, echo = FALSE, error=FALSE, cache=FALSE}

reg1 = lm(
  log(price) ~ twoPlayer + log(player.transport_cost),
  df
)

summary(reg1)
```


- Where $P_{ip}$ is the average price for for this participant in this period, the average of 20 sub-periods. 
- $\delta_{i}$ is an indicator equal to 1 if individual $i$ participated in the two-player treatment.
- $S_ip$ is the shopping cost this individual faced in this period. 
- where $Period_p$ is the period number. 

In this specification, the coefficient $\beta_2$ measures the average effect of being assigned to the less competitive two-player treatment group. With $\beta_2 = 0.350138$, a 1% increase in shopping costs leads to a 0.35% increase in prices. This is significant. 

# Hypothesis 3 - mark-up responsiveness to competition 

**Hypothesis 3**. *Mark-ups will be less responsive to changes in shopping costs in less competitive (lower N) markets.*

$ln(Price_{(i,p)}) = \beta_0 + \beta_1 \delta_{2p} + \beta_2 ln(ShoppingCost) + \beta_3 \delta_{i} ln(ShoppingCost)  + \epsilon_{(i,p)}$

```{r, message = FALSE, warning = FALSE, echo = FALSE, error=FALSE, cache=FALSE}

reg2 = lm(
  log(price) ~ twoPlayer + log(player.transport_cost) + twoPlayer:log(player.transport_cost) ,
  df
)

summary(reg2)
```



The coefficient $\beta_2$ estimates that a 1% increase in shopping costs will leave to a 0.45% increase in prices in the four-player game. The $\beta_3$ coefficient indicates *a one unit increase in shopping cost leads to a 28% decrease in prices in the two-player game relative to the 4-player game*". 

We have strong evidence that mark-ups are less responsive to tranpostation cost changes in the less competitive treatment than the more competitive treatment. 

```{r, message = FALSE, warning = FALSE, echo = FALSE, error=FALSE, cache=FALSE}

# library(memisc)
# library(pander)
# 
# mytable <- mtable(
#   'Model 1' = reg1,
#   'Model 2' = reg2,
#   summary.stats = c('R-squared','F','p','N'))
# 
# (mytable)
```


| Dependent Var: $ln(P_{ip})$              | Model 1  |  | Model 2    | |
|------------------------------------------|:--------------:|:--:|:------------:|:----:|
|  $\delta_{i}$ (two-player)               | 0.897   | \*\*\* |  0.653    | \*\*\*  |
|                                          | (0.049) |        | (0.068)   | |
|  $ln(ShoppingCost)$                      | 0.347   | \*\*\* | 0.454     | \*\*\*  | 
|                                          | (0.028) |        | (0.034)   | |
|  $\delta_{i} \cdot ln(ShoppingCost)$     |         |        | -0.282    | \*\*\* |  
|                                          |         |        | (0.055)   |   |
|                                          |         |        |           | | 
| --------------------------------------- | ------ | --- | ------ | --- |
|  N                                        | 552    |  | 552     |  |

# Hypothesis 4 - Collusion and Shopping Costs

**Hypothesis 4**. *Collusion will be easier to form in low shopping cost environments*

Define collusion

## Idea 1 - Joint positive profits. 

A subject is said to be 'colluding' when they and their adjacent players have jointly positive profits. 
    - In the save of the two-player game, both players' profits are positive. In the case of the four-player game, the profits of the two players to the left and right (circle marketplace) are positive. 
    - This poses of problem in comparing "collusion" between two and four-player games. So we should not do that. 
- Look at violines for bit - bi-modal splits in distribution. 


```{r, message = FALSE, warning = FALSE, echo = FALSE, error=FALSE, cache=FALSE}

df = sesDat2p %>%
  dplyr::filter(
    player.transport_cost != 0.25
  ) %>%
  group_by(session.code,player.transport_cost,player.transport_cost) %>%
  dplyr::mutate(
    numPlayer = "Two-Player",
    profit = (player.round_payoff * max(subsession.round_number)),
    player.loc = paste("Loc",player.loc, sep="")
  ) %>%
  ungroup() %>%
  arrange(session.code, player.period_number, subsession.round_number,group.id_in_subsession, player.loc) %>%
  dplyr::select(numPlayer, session.code, player.transport_cost, player.period_number, subsession.round_number, group.id_in_subsession, player.loc, profit)
  
df2p = df %>%
  group_by(group.id_in_subsession) %>%
  spread(player.loc, profit) %>%
  mutate(
    joinPosProfit = ifelse(Loc0.25 > 0 & Loc0.75 > 0, 1, 0)
  )



df4p = sesDat4p %>%
  group_by(session.code,player.transport_cost,player.transport_cost) %>%
  dplyr::mutate(
    numPlayer = "Four-Player",
    profit = (player.round_payoff),
    player.loc = paste("Loc",player.loc, sep="")
  ) %>%
  ungroup() %>%
  arrange(session.code, player.period_number, subsession.round_number,group.id_in_subsession, player.loc) %>%
  dplyr::select(numPlayer, session.code, player.transport_cost, player.period_number, subsession.round_number, group.id_in_subsession, player.loc, profit)




df4p = df4p %>%
  group_by(group.id_in_subsession) %>%
  spread(player.loc, profit) %>%
  mutate(
    joinPosProfit = ifelse(Loc0.125 > 0 & Loc0.375 & Loc0.625 > 0 & Loc0.875 > 0, 1, 0)
  )


df2 = bind_rows(
  df4p, df2p
)




kable(
  format = "markdown", 
  bind_rows(
    df2p %>%
    group_by(numPlayer, player.transport_cost) %>%
    summarise(
      joinPosProfit_mean = mean(joinPosProfit),
      n = length(unique(paste(group.id_in_subsession ,player.period_number)))
    ),
    df4p %>%
    group_by(numPlayer, player.transport_cost) %>%
    summarise(
      joinPosProfit_mean = mean(joinPosProfit),
      n = length(unique(paste(group.id_in_subsession ,player.period_number)))
    )
  ),  
  align = c("c"),
  col.names = c("","Shopping Cost","Percent of Period Joint Positive Profits","Period Group Obvservation")
)


```

```{r, message = FALSE, warning = FALSE, echo = FALSE, error=FALSE, cache=FALSE}



ggplot(
  df2 %>% 
    group_by(numPlayer, player.period_number, group.id_in_subsession) %>%
    dplyr::summarise(
      joinPosProfit = mean(joinPosProfit),
      player.transport_cost = unique(player.transport_cost)
    )
) +
  facet_grid(numPlayer ~.) +
  geom_violin(
    aes(y = joinPosProfit,
        x = player.transport_cost,
        group = player.transport_cost),
    alpha = 0.3,
    color = "grey70"
  ) +
  geom_ribbon(
    data = df2 %>% 
      group_by(numPlayer, player.transport_cost) %>%
      summarise(
        mean_joinPosProfit = mean(joinPosProfit),
        joinPosProfit_se_Up1 = mean_joinPosProfit + se(joinPosProfit),
        joinPosProfit_se_Dwn1 = mean_joinPosProfit - se(joinPosProfit)
      ), 
    aes(
      x = player.transport_cost,
      ymax = joinPosProfit_se_Up1,
      ymin = joinPosProfit_se_Dwn1
    ),
    alpha = .2
  ) +
  geom_line(
    data = df2 %>% 
      group_by(numPlayer, player.transport_cost) %>%
      summarise(
        mean_joinPosProfit = mean(joinPosProfit)
      )  , 
    aes(
      x = player.transport_cost,
      y = mean_joinPosProfit
    )
  ) +
  geom_jitter(
    aes(
      y = joinPosProfit,
      x = player.transport_cost
    ),
    width = 0.02,
    height = 0,
    alpha = 0.3) + 
  scale_x_continuous(
    breaks = c(0.1, 0.25, 0.5, 0.75, 1.0)
  ) +
  theme_bw() +
  labs(
    x = "Shopping Cost",
    y = "Percent of Period with Joint Positive Profits",
    title = "Joint Positive Profits"
  )


```

There is visually suggestive evidence that with higher shopping costs, groups are better able to collude. 


## Idea 2 - Just look at profits. 

Are profits higher? 
    - Perhaps too linked to the discussion in Hypothesis 1-3. 


```{r, echo=FALSE}

df =  sesDat2p %>%
  ungroup() %>%
  group_by(session.code, participant.code, player.transport_cost,player.period_number) %>%
  mutate(
    player.round_payoff = player.round_payoff * max(subsession.round_number) #deal with f'ing t=0.25...
  ) %>%
   summarise(
     mean_profit = mean(player.round_payoff)
   ) %>%
  mutate(
    NumPlayers = "two-players"
  )

df = bind_rows(
  df, 
  (  sesDat4p %>%
       group_by(session.code,player.transport_cost) %>%
       group_by(session.code, participant.code, player.transport_cost,player.period_number) %>% 
       summarise(
         mean_profit = mean(player.round_payoff * max(subsession.round_number))
       ) %>%
       filter(
         !is.na(mean_profit)
       ) %>%
       mutate(
         NumPlayers = "four-players"
       )
  )
)

df2 = df %>%
  group_by(
    player.transport_cost, NumPlayers
  ) %>%
  summarise(
    mean_profit = mean(mean_profit)
  )

ggplot(
 df
) +
    geom_violin(
    aes(
      x = (player.transport_cost),
      y = mean_profit,
      group = player.transport_cost
    ), alpha = .8
  ) +
  geom_jitter(
    aes(
      x = (player.transport_cost),
      y = mean_profit
    ), 
    alpha = .3,
    width = .05, height = 0
  ) +
  geom_line(
    data = df2,
    aes(
      y = (mean_profit), 
      x = (player.transport_cost))
  ) +
  facet_grid(NumPlayers~.) +
  theme_bw() +
  labs(
    x = "Shopping Cost",
    y = "Average Period Profit",
    title = "Average Period Profits and Shopping Costs"
  )




```

## to do for collusion 

Tailing thing; 

- get into more simple dynamics of collusion.... 


---- 

```{r, echo=F, results='asis'}

cat(
  " Compiled by Curtis Kephart, curtis.kephart@nyu.edu, ",
  " with [R Markdown](http://rmarkdown.rstudio.com) Notebook. ",
  sep = ""
)
```

```{r, echo=F, results='asis'}

cat(
  as.character(Sys.time())," GMT, ",
  Sys.timezone(location = TRUE),
  sep = ""
)
```
