---
title: "On the dynamics of mark-ups, results section"
author: 
- "Curtis Kephart"
- "David Munro"
output:
  html_document:
    toc: yes
    toc_depth: 2
  pdf_document:
    toc: yes
    toc_depth: 2
    fig_height: 4
    fig_width: 7
  html_notebook:
    toc: yes
    toc_depth: 2
editor_options: 
  chunk_output_type: inline
---


To Do List

- ADD  a first half second half indicator - done, see field `period_half`.
- Code that runs. 
- Get github up and running


```{r util, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
knitr::opts_chunk$set(cache=TRUE ) 
#make sure you set the working directory to the project directory. 

```
 

```{r, setup, echo=FALSE, error=FALSE,  message=FALSE, warning=FALSE, cache=FALSE, include=FALSE}
library(dplyr)
library(ggplot2)
library(knitr)
library(tidyr)
library(reshape2)
library(glue)

source("../r/etl.R")

sessDat = sessDat %>% 
  ungroup() %>% 
  group_by(participant.code, player.period_number) %>% 
  mutate(
    playerNum = group_size_str,
    score_subperiod = lead(player.prev_round_payoff),
    score_total = lead(player.prev_round_cumulative_payoff)
  )

```


# Data

The object `sessDat` has data from all 6 sessions. 

- There are `r sessDat$participant.code %>% unique() %>% length` subjects
- Each subject participated in 15 rounds. 
- Each round had 20 subperiods. The data lists 22 subperiods. 
 - Subperiod `0` is the settings `player.loc` and `player.price` the subject was initialized at. 
 - Subperiod `21` is the `player.price` the subject would be at if the period continued. 

Variables in `sessDat`

- `session.code`
- `participant.code` is a unique subject identifyer.
- `player.period_number`
- `player.subperiod_number`
- `period_half` either "First Half" or "Second Half". `NA` if period 0 or 21.  
- `player.loc`  location
- `player.price` price
- `player.boundary_lo` and `player.boundary_hi` are the high and low boundary for this player currently
- `group_size` number of players in the group
- `group_size_str` a string for the group size
- `player.transport_cost` shopping cost, `0.10, 0.25, 0.40, 0.60`
- `player.mc` mill cost, `0.05, 0.15, 0.25`
- `player.rp` reserve price, `0.8, 0.9, 1.0`
- `score_subperiod` this player's current score
- `score_total` currency period's total score for this player. 


# Summary Statistics

Summary of sessions and subjects.

```{r, message = FALSE, warning = FALSE, echo = FALSE, error=FALSE,  cache=FALSE}


sessDat %>%
  group_by(group_size_str) %>%
  summarise(
    Sessions = session.code %>% unique %>% length,
    Subjects = participant.code %>% unique %>% length,
    Periods  = player.period_number %>% unique %>% length 
  ) %>%
  kable(
    format = "markdown",
    align = c("l","c","c","c"),
    col.names = c("Number of Players", "Sessions", "Subjects", "Periods Per Session")
  )

```


Sessions were run at the New York University Abu Dhabi and the United Arab Emirates with undergraduate students between Oct 17 and Oct 19th, 2017. 

Subjects earned on average \$`r -30 + (SsPay %>% filter(!(Payment %in% c(0,30))))$Payment %>% mean %>% round(2)` from the experiment. After a 30 AED show-up fee and rounding up to the 5 AED, subjects walked away on average with \$`r (SsPay %>% filter(!(Payment %in% c(0,30))))$Payment %>% mean %>% round(2)`

The experiment was conducted with oTree (*Citation: Chen, D.L., Schonger, M., Wickens, C., 2016. oTree - An open-source platform for laboratory, online and field experiments. Journal of Behavioral and Experimental Finance, vol 9: 88-97*) subjects were recruited with hroot (*Citation: Bock, Olaf, Ingmar Baetge & Andreas Nicklisch (2014). hroot – Hamburg registration and organization online tool. European Economic Review 71, 117-120*)




# Hypothesis 1 - competitiveness and mark-ups

**Hypothesis 1**. *Static mark-ups will be lower in more competitive (higher N) markets.*

In the plot below, 

- Each dot is the average price per subject in one period-half (20 subperiods, two halfs) with fixed shopping costs and player count. 
- Violins are similarly based on average player-period prices. 
- The line is the average price for that player-number period-half combination, 
- Ribben is the confidence interval, one se plus or minus. 


```{r, message = FALSE, warning = FALSE, echo = FALSE, error=FALSE,  cache=FALSE}
avg_per_prices <- function(
  data = sessDat,
  rp = NULL
){
  df = sessDat %>%
  filter(
    !is.na(period_half)
    & player.rp == rp
  )

df2 = df %>%
  group_by(group_size_str, player.transport_cost, player.period_number, participant.code,period_half, player.mc) %>%
  dplyr::summarise(
    Price = mean(player.price),
    Price_Median = median(player.price),
    price_se_Up1 = Price + se(player.price),
    price_se_Dwn1 = Price - se(player.price)
  )

p1 = df %>%
  ggplot(
  ) +
  facet_grid(group_size_str ~ period_half) +
  geom_violin(
    aes(y = player.price,
        x = player.transport_cost,
        group = player.transport_cost),
    alpha = 0.3,
    color = "grey70"
  ) +
  geom_ribbon(
    data = df2 %>% 
      group_by(group_size_str, player.transport_cost, player.mc, period_half) %>%
      summarise(
        mean_price = mean(Price),
        price_se_Up1 = mean_price + se(Price),
        price_se_Dwn1 = mean_price - se(Price)
      ), 
    aes(
      x = player.transport_cost,
      ymax = price_se_Up1,
      ymin = price_se_Dwn1,
      group = player.mc,
      fill = player.mc
      
    ),
    alpha = .2
  ) +
  geom_line(
    data = df2 %>% 
      group_by(group_size_str, player.transport_cost, player.mc, period_half) %>%
      summarise(
        mean_price = mean(Price)
      )  , 
    aes(
      x = player.transport_cost,
      y = mean_price,
      group = player.mc,
      color = player.mc
    )
  ) +
  geom_jitter(
    aes(
      y = Price,
      x = player.transport_cost
    ),
    
    data = df2,
    width = 0.02,
    height = 0,
    alpha = 0.2) + 
  scale_x_continuous(
    breaks = c(0.1, 0.25, 0.4, 0.6)
  ) +
  theme_bw() +
  labs(
    x = "Shopping Cost",
    y = "Price",
    title = glue("Average Period Prices, RP: {rp}")
  )

return(p1)
  
}

avg_per_prices(rp = 1.0)
avg_per_prices(rp = 0.9)
avg_per_prices(rp = 0.8)



```

In the pilot we had a spread of transport costs from 0.1 to 1.0. Between 0.1 and 0.5 there wasn't a huge difference in price, only at 0.75 and 1.0 did we see a substantial increase in markups. In this design we only had a spread of transport costs between 0.1 and 0.6, and we don't see a consistent increase in price as transport costs increase. 

- RP 0.9 is interesting. 

---------

In the plot below, 

- each dot is the average price per subject in one period (20 subperiods) with fixed shopping costs and player count. 
- violins are based on average player-period prices. 
- the line is the average price for that player-number, shopping cost comvination, 
- ribben is the confidence interval, one se plus or minus. 
- A very similar plot appears when looking at all prices over all subperiods. 


```{r, message = FALSE, warning = FALSE, echo = FALSE, error=FALSE,  cache=FALSE}

df2 = sessDat %>%
  filter(!is.na(period_half)) %>% 
  group_by(playerNum, period_half, player.transport_cost, player.period_number, participant.code) %>%
  dplyr::summarise(
    Price = mean(player.price),
    Price_Median = median(player.price),
    price_se_Up1 = Price + se(player.price),
    price_se_Dwn1 = Price - se(player.price)
  )



ggplot(
  df2
) +
  facet_grid(playerNum ~ period_half) +
  geom_violin(
    aes(y = Price,
        x = player.transport_cost,
        group = player.transport_cost),
    alpha = 0.3,
    color = "grey70"
  ) +
  geom_ribbon(
    data = df2 %>% 
      group_by(playerNum, player.transport_cost) %>%
      summarise(
        mean_price = mean(Price),
        price_se_Up1 = mean_price + se(Price),
        price_se_Dwn1 = mean_price - se(Price)
      ), 
    aes(
      x = player.transport_cost,
      ymax = price_se_Up1,
      ymin = price_se_Dwn1
    ),
    alpha = .2
  ) +
  geom_line(
    data = df2 %>% 
      group_by(playerNum, player.transport_cost) %>%
      summarise(
        mean_price = mean(Price)
      )  , 
    aes(
      x = player.transport_cost,
      y = mean_price
    )
  ) +
  geom_jitter(
    aes(
      y = Price,
      x = player.transport_cost
    ),
    
    data = df2,
    width = 0.02,
    height = 0,
    alpha = 0.3) + 
  scale_x_continuous(
    breaks = c(0.1, 0.25, 0.5, 0.75, 1.0)
  ) +
  theme_bw() +
  labs(
    x = "Shopping Cost",
    y = "Price",
    title = "Average Period Prices"
  )





  
```


----------

Comparing prices in both treatments. 
- We see with greater competition there are lower prices accross all shopping costs. 

```{r, message = FALSE, warning = FALSE, echo = FALSE, error=FALSE,  cache=FALSE}


df2 = sessDat %>%  
  filter(!is.na(period_half)) %>% 
  group_by(playerNum, player.transport_cost, participant.code, player.period_number) %>%
  dplyr::summarise(
    player.price = mean(player.price)
  ) %>%
  group_by(playerNum, player.transport_cost) %>%
  dplyr::summarise(
    Price = paste(mean(player.price) %>% round(2), " (±", se(player.price) %>% round(4),  ")", sep="")
  )

kable(
  format = "markdown",
  df2 %>%tidyr::spread(
    player.transport_cost, Price
  ),
  align = c("l","c","c","c","c","c"),
  # col.names = c("", "s = 0.1","s = 0.25","s = 0.5","s = 0.75","s = 1"),
  caption = "adsfse"
)

```

Now, looking just at the later half of each period, subperiods 11 to 20, (remove from final)

```{r, message = FALSE, warning = FALSE, echo = FALSE, error=FALSE,  cache=FALSE}

df2 = sessDat %>%  
  filter(!is.na(period_half)) %>% 
  group_by(playerNum, player.transport_cost, participant.code, player.period_number) %>%
  dplyr::summarise(
    player.price = mean(player.price)
  ) %>%
  group_by(playerNum, player.transport_cost) %>%
  dplyr::summarise(
    Price = paste(mean(player.price) %>% round(2), " (±", se(player.price) %>% round(4),  ")", sep="")
  )

kable(
  format = "markdown",
  df2 %>%tidyr::spread(
    player.transport_cost, Price
  ),
  align = c("l","c","c","c","c","c"),
  # col.names = c("", "t = 0.1","t = 0.25","t = 0.5","t = 0.75","t = 1"),
  caption = "adsfse"
)

```


Strong evidence for Hypothesis 1. 

- Looking at the average prices within a period (all 20 subperiods) with the same player number and transport cost, there is a statistically significant difference between prices at each transport level between player number treatments. 


- Even comparing `t = 6.0` in the four player game -- the transport cost in which the four-player game with highest prices --
to `t = 0.25` in the two player game -- in which prices were the lowest in the two-player game -- the two player game has statistically significantly higher prices (p-value < 0.001). 


```{r, message = FALSE, warning = FALSE, echo = FALSE, error=FALSE,  cache=FALSE}

df2 = sessDat %>%  
  group_by(playerNum, player.transport_cost, participant.code, player.period_number) %>%
  dplyr::summarise(
    player.price = mean(player.price)
  )
# 0.10, 0.25, 0.40, 0.60`


with(df2, 
     t.test(player.price[(playerNum == "Two Player" & player.transport_cost == 0.25)],
            player.price[(playerNum == "Four Player" & player.transport_cost == 0.6)]
     )
)
with(df2, 
     wilcox.test(player.price[(playerNum == "Two Player" & player.transport_cost == 0.25)], 
            player.price[(playerNum == "Four Player" & player.transport_cost == 0.6)]
     )
)


```

# Hypothesis 2 - shipping costs and mark-ups

**Hypothesis 2** - *There is a positive relationship between shopping costs and mark-ups.*

### Looking at the two-player game

```{r, message = FALSE, warning = FALSE, echo = FALSE, error=FALSE,  cache=FALSE}
# two player

df2 = sessDat %>%
    dplyr::filter(
      playerNum == "Two Player",
      !is.na(period_half)
      )%>%
  group_by(playerNum, player.transport_cost, player.period_number, participant.code, period_half) %>%
  dplyr::summarise(
    Price = mean(player.price),
    Price_Median = median(player.price),
    price_se_Up1 = Price + se(player.price),
    price_se_Dwn1 = Price - se(player.price)
  )
#`0.10, 0.25, 0.40, 0.60`

p1 = ggplot(
  df2
) +
  
  facet_grid(period_half ~ .) +
  geom_violin(
    aes(y = Price,
        x = player.transport_cost,
        group = player.transport_cost),
    alpha = 0.3,
    color = "grey70"
  ) +
  geom_ribbon(
    data = df2 %>% 
      group_by(playerNum, player.transport_cost) %>%
      summarise(
        mean_price = mean(Price),
        price_se_Up1 = mean_price + se(Price),
        price_se_Dwn1 = mean_price - se(Price)
      ), 
    aes(
      x = player.transport_cost,
      ymax = price_se_Up1,
      ymin = price_se_Dwn1
    ),
    alpha = .2
  ) +
  geom_line(
    data = df2 %>% 
      group_by(playerNum, player.transport_cost) %>%
      summarise(
        mean_price = mean(Price)
      )  , 
    aes(
      x = player.transport_cost,
      y = mean_price
    )
  ) +
  geom_jitter(
    aes(
      y = Price,
      x = player.transport_cost
    ),
    
    data = df2,
    width = 0.02,
    height = 0,
    alpha = 0.3) + 
  scale_x_continuous(
    breaks = c(0.1, 0.25, 0.4, 0.6)
  ) +
  theme_bw() +
  labs(
    x = "Shopping Cost",
    y = "Price",
    title = "Average Period Prices - Two Players"
  ) +
  coord_cartesian(xlim = c(0,0.7), ylim = c(0,1)) 
p1
```

```{r, message = FALSE, warning = FALSE, echo = FALSE, error=FALSE,  cache=FALSE}
# Four player

df2 = sessDat %>%
      dplyr::filter(
      playerNum == "Four Player",
      !is.na(period_half)
      )%>%
  group_by(playerNum, player.transport_cost, player.period_number, participant.code, period_half) %>%
  dplyr::summarise(
    Price = mean(player.price),
    Price_Median = median(player.price),
    price_se_Up1 = Price + se(player.price),
    price_se_Dwn1 = Price - se(player.price)
  )



p2 = ggplot(
  df2
) +
  facet_grid(period_half ~ .) +
  geom_violin(
    aes(y = Price,
        x = player.transport_cost,
        group = player.transport_cost),
    alpha = 0.3,
    color = "grey70"
  ) +
  geom_ribbon(
    data = df2 %>% 
      group_by(playerNum, player.transport_cost) %>%
      summarise(
        mean_price = mean(Price),
        price_se_Up1 = mean_price + se(Price),
        price_se_Dwn1 = mean_price - se(Price)
      ), 
    aes(
      x = player.transport_cost,
      ymax = price_se_Up1,
      ymin = price_se_Dwn1
    ),
    alpha = .2
  ) +
  geom_line(
    data = df2 %>% 
      group_by(playerNum, player.transport_cost) %>%
      summarise(
        mean_price = mean(Price)
      )  , 
    aes(
      x = player.transport_cost,
      y = mean_price
    )
  ) +
  geom_jitter(
    aes(
      y = Price,
      x = player.transport_cost
    ),
    
    data = df2,
    width = 0.02,
    height = 0,
    alpha = 0.3) + 
  scale_x_continuous(
    breaks = c(0.1, 0.25, 0.4, 0.6)
  ) +
  theme_bw() +
  labs(
    x = "Shopping Cost",
    y = "Price",
    title = "Average Period Prices - Four Players"
  ) +
  coord_cartesian(xlim = c(0,0.7), ylim = c(0,1)) 
p2

```



```{r, echo = F, eval = T, tidy = T}

df = sessDat %>%
  filter(
    !is.na(period_half)
  ) %>% 
  group_by(playerNum, player.transport_cost, player.period_number, participant.code) %>%
  dplyr::summarise(
    Price = mean(player.price)
  )

df = df %>%
  ungroup() %>%
  group_by(playerNum, player.transport_cost) %>%
  summarise(
    n=n(),
    mean_price = mean(Price) %>% round(3),  
    median_price = median(Price) %>% round(3),
    se_price = (sd(Price)/(n)^0.5)  %>% round(3)
  ) 

kable(
  format = "markdown", 
  df,  align = c("c"),
  col.names = c("","Shopping Cost","N","Mean Price","Median Price","Standard Error")
)
```

Recall there were `r sessDat %>% filter(playerNum == "Four Player") %>% ungroup %>% distinct(participant.code) %>% nrow` subjects in the four-player treatment and `r sessDat %>% filter(playerNum == "Two Player") %>% ungroup %>% distinct(participant.code) %>% nrow` subjects in the two-player treatment. 


## Initial Look at Two-Player Game

First, within the two player game, comparing prices in `t = 0.1` and `t = 0.6` (see below), there is to be a statistically significant difference. 

There is a relationship between prices and shopping cost treatments. In higher shopping cost settings subjects tended to have higher prices. 

- Unit of observation is an individual's average price within a period, at a set shopping cost level. 
- A t test comparing prices between min and max shopping costs. Prices are average price at the session, participant, and period level. P-value 2.867e-11
- A MW rank sum test comparing prices between min and max shopping costs. Prices are average price at the session, participant, and period level. P-value 1.12e-09

```{r, echo=FALSE}
df =  sessDat %>%
  filter(
    !is.na(period_half),
    playerNum == "Two Player"
  ) %>% 
  ungroup() %>%
  group_by(session.code, participant.code, player.period_number, player.transport_cost) %>%
   summarise(
     mean_price = mean(player.price)
   )
with(df, t.test(mean_price[player.transport_cost == 0.1], mean_price[player.transport_cost == 0.6]))
with(df, wilcox.test(mean_price[player.transport_cost == 0.1], mean_price[player.transport_cost == 0.6]))

```



## Initial Look at Four-Player Game

In the four-player game the relationship, at least between the lowest and highest shopping cost, does not appear stronger.

- A t test comparing prices between min and max shopping costs. Prices are average price at the session, participant, and period level. P-value 0.9459.
- A MW rank sum test comparing prices between min and max shopping costs. Prices are average price at the session, participant, and period level. P-value = 0.8919


```{r, echo=FALSE}
df = sessDat %>%
  filter(
    !is.na(period_half),
    playerNum == "Four Player"
  ) %>% 
  ungroup() %>%
  group_by(session.code, participant.code, player.transport_cost,player.period_number) %>%
   summarise(
     mean_price = mean(player.price)
   )
with(df, t.test(mean_price[player.transport_cost == 0.1], mean_price[player.transport_cost == 0.6]))
with(df, wilcox.test(mean_price[player.transport_cost == 0.1], mean_price[player.transport_cost == 0.6]))

```


## Model

Only looking at the first half of periods

```{r, message = FALSE, warning = FALSE, echo = FALSE, error=FALSE, cache=FALSE}

df = sessDat %>% 
  filter(
    !is.na(period_half),
    period_half == "First Half"
  ) %>% 
  ungroup() %>%
  group_by(playerNum, session.code, participant.code, player.period_number, player.transport_cost) %>%
  summarise(
    price = mean(player.price),
    median_price = median(player.price)
  )

p1= ggplot(
  df,
  aes(
    x = player.transport_cost,
    y = price,
    group = playerNum,
    color = playerNum
  )
) +
  geom_jitter(
    aes(y = price),
    width = 0.07,
    alpha = .1) +
  geom_smooth(method = "lm") +
  theme_bw() +
  labs(
    x = "Shopping Cost",
    y = "Price"
    
  )
p1
```

Here we have a log-log model regressing prices on shopping costs, with player-number fixed effects. 

$ln(P_{ip}) = \beta_0 + \beta_1 \delta_{i} + \beta_2 ln(S_{ip}) + \beta_3 Period_p + \epsilon_{(ip)}$

```{r, message = FALSE, warning = FALSE, echo = FALSE, error=FALSE, cache=FALSE}

reg1 = lm(
  log(price) ~ playerNum + log(player.transport_cost) + player.period_number,
  data = df %>% mutate(price = price + 0.01)
)

summary(reg1)
```


- Where $P_{ip}$ is the average price for for this participant in this period, the average of 20 sub-periods. 
- $\delta_{i}$ is an indicator equal to 1 if individual $i$ participated in the two-player treatment.
- $S_ip$ is the shopping cost this individual faced in this period. 
- where $Period_p$ is the period number. Period fixed effects. 

In this specification, the coefficient $\beta_2$ measures the average effect of being assigned to the less competitive two-player treatment group. With $\beta_2 = -0.056040$, a 1% increase in shopping costs leads to a -5.6% decrease in prices. This is significant. 

# Hypothesis 3 - mark-up responsiveness to competition 

**Hypothesis 3**. *Mark-ups will be less responsive to changes in shopping costs in less competitive (lower N) markets.*

$ln(Price_{(i,p)}) = \beta_0 + \beta_1 \delta_{2p} + \beta_2 ln(ShoppingCost) + \beta_3 \delta_{i} ln(ShoppingCost)  + \epsilon_{(i,p)}$

```{r, message = FALSE, warning = FALSE, echo = FALSE, error=FALSE, cache=FALSE}

reg2 = lm(
  log(price) ~ playerNum + log(player.transport_cost) + playerNum:log(player.transport_cost) ,
  data = df %>% mutate(price = price + 0.01)
)

summary(reg2)
```



The coefficient $\beta_2$ estimates that a 1% increase in shopping costs will leave to a 3.4% decrease in prices in the four-player game. The $\beta_3$ coefficient indicates *a one unit increase in shopping cost leads to a 5.9% decrease in prices in the two-player game relative to the 4-player game*". 

```{r, message = FALSE, warning = FALSE, echo = FALSE, error=FALSE, cache=FALSE}

# library(memisc)
# library(pander)
# 
# mytable <- mtable(
#   'Model 1' = reg1,
#   'Model 2' = reg2,
#   summary.stats = c('R-squared','F','p','N'))
# 
# (mytable)
```


| Dependent Var: $ln(P_{ip})$              | Model 1  |  | Model 2    | |
|------------------------------------------|:--------------:|:--:|:------------:|:----:|
|  $\delta_{i}$ (two-player)               | 0.559101    | \*\*\* |  0.45058    | \*\*\*  |
|                                          | (0.015870)  |        | (0.04155)   | |
|  $ln(ShoppingCost)$                      | -0.056040   | \*\*\* | -0.04844     | \*\*\*  | 
|                                          | (0.011023)  |        | (0.01558)   | |
|  $\delta_{i} \cdot ln(ShoppingCost)$     |             |        | -0.05857    | \* |  
|                                          |             |        | (0.02464)   |   |
|                                          |             |        |           | | 
| --------------------------------------- | ------ | --- | ------ | --- |
|  N                                        | 552    |  | 552     |  |

# Hypothesis 4 - Collusion and Shopping Costs

**Hypothesis 4**. *Collusion will be easier to form in low shopping cost environments*

Define collusion

## Idea 1 - Joint positive profits. 

A subject is said to be 'colluding' when they and their adjacent players have jointly positive profits. 
    - In the save of the two-player game, both players' profits are positive. In the case of the four-player game, the profits of the two players to the left and right (circle marketplace) are positive. 
    - This poses of problem in comparing "collusion" between two and four-player games. So we should not do that. 
- Look at violines for bit - bi-modal splits in distribution. 


```{r, message = FALSE, warning = FALSE, echo = FALSE, error=FALSE, cache=FALSE}

df = sessDat %>%
  dplyr::filter(
    player.subperiod_number > 0,
    player.subperiod_number < 21
  ) %>%
  group_by(playerNum, session.code,player.transport_cost,playerNum) %>%
  dplyr::mutate(
    profit = score_subperiod,
    player.loc = paste("Loc",player.loc, sep="")
  ) %>%
  ungroup() %>%
  arrange(playerNum, session.code, player.period_number, player.period_number, player.subperiod_number,group.id_in_subsession, player.loc) %>%
  dplyr::select(playerNum, session.code, player.transport_cost, player.period_number, player.subperiod_number, group.id_in_subsession, player.loc, profit)
  
df2p = df %>%
  filter(playerNum == "Two Player") %>% 
  group_by(group.id_in_subsession, player.period_number, player.subperiod_number) %>%
  spread(player.loc, profit) %>%
  mutate(
    joinPosProfit = ifelse(Loc0.25 > 0 & Loc0.75 > 0, 1, 0)
  )

df4p = df %>%
  filter(playerNum == "Four Player") %>% 
  group_by(group.id_in_subsession) %>%
  spread(player.loc, profit) %>%
  mutate(
    joinPosProfit = ifelse(Loc0.125 > 0 & Loc0.375 & Loc0.625 > 0 & Loc0.875 > 0, 1, 0)
  )


df2 = bind_rows(
  df4p, df2p
)




kable(
  format = "markdown", 
  bind_rows(
    df2p %>%
    group_by(playerNum, player.transport_cost) %>%
    summarise(
      joinPosProfit_mean = mean(joinPosProfit),
      n = length(unique(paste(group.id_in_subsession ,player.period_number)))
    ),
    df4p %>%
    group_by(playerNum, player.transport_cost) %>%
    summarise(
      joinPosProfit_mean = mean(joinPosProfit),
      n = length(unique(paste(group.id_in_subsession ,player.period_number)))
    )
  ),  
  align = c("c"),
  col.names = c("","Shopping Cost","Percent of Period Joint Positive Profits","Period Group Obvservation")
)


```

```{r, message = FALSE, warning = FALSE, echo = FALSE, error=FALSE, cache=FALSE}



ggplot(
  df2 %>% 
    group_by(playerNum, player.period_number, player.transport_cost, group.id_in_subsession) %>%
    dplyr::summarise(
      joinPosProfit = mean(joinPosProfit)
    )
) +
  facet_grid(playerNum ~.) +
  geom_violin(
    aes(y = joinPosProfit,
        x = player.transport_cost,
        group = player.transport_cost),
    alpha = 0.3,
    color = "grey70"
  ) +
  geom_ribbon(
    data = df2 %>% 
      group_by(playerNum, player.transport_cost) %>%
      summarise(
        mean_joinPosProfit = mean(joinPosProfit),
        joinPosProfit_se_Up1 = mean_joinPosProfit + se(joinPosProfit),
        joinPosProfit_se_Dwn1 = mean_joinPosProfit - se(joinPosProfit)
      ), 
    aes(
      x = player.transport_cost,
      ymax = joinPosProfit_se_Up1,
      ymin = joinPosProfit_se_Dwn1
    ),
    alpha = .2
  ) +
  geom_line(
    data = df2 %>% 
      group_by(playerNum, player.transport_cost) %>%
      summarise(
        mean_joinPosProfit = mean(joinPosProfit)
      )  , 
    aes(
      x = player.transport_cost,
      y = mean_joinPosProfit
    )
  ) +
  geom_jitter(
    aes(
      y = joinPosProfit,
      x = player.transport_cost
    ),
    width = 0.02,
    height = 0,
    alpha = 0.3) + 
  scale_x_continuous(
    breaks = c(0.1, 0.25, 0.4, .6)
  ) +
  theme_bw() +
  labs(
    x = "Shopping Cost",
    y = "Percent of Period with Joint Positive Profits",
    title = "Joint Positive Profits"
  )


```

There is visually suggestive evidence that with higher shopping costs, groups are better able to collude. 


## Idea 2 - Just look at profits. 

Are profits higher? 
    - Perhaps too linked to the discussion in Hypothesis 1-3. 


```{r, echo=FALSE}

df =  sessDat %>%
  filter(
    player.period_number > 0 
    & player.period_number < 21
    & !is.na(period_half)) %>% 
  ungroup() %>%
  group_by(playerNum, period_half, session.code, participant.code, player.transport_cost,player.period_number) %>%
   summarise(
     mean_profit = mean(score_subperiod)
   )

df2 = df %>% 
  group_by(playerNum, period_half, player.transport_cost) %>% 
  summarise(
    mean_profit = mean(mean_profit)
  )

ggplot(
 df
) +
  facet_grid(playerNum ~ period_half) +
    geom_violin(
    aes(
      x = (player.transport_cost),
      y = mean_profit,
      group = player.transport_cost
    ), alpha = .8
  ) +
  geom_jitter(
    aes(
      x = (player.transport_cost),
      y = mean_profit
    ), 
    alpha = .1,
    width = .05, height = 0
  ) +
  geom_line(
    data = df2,
    aes(
      y = mean_profit, 
      x = (player.transport_cost))
  ) +
  theme_bw() +
  labs(
    x = "Shopping Cost",
    y = "Average Period Profit",
    title = "Average Period Profits and Shopping Costs"
  )




```

## to do for collusion 

Tailing thing; 

- get into more simple dynamics of collusion.... 


---- 

```{r, echo=F, results='asis'}

cat(
  " Compiled by Curtis Kephart, curtis.kephart@nyu.edu, ",
  " with [R Markdown](http://rmarkdown.rstudio.com) Notebook. ",
  sep = ""
)
```

```{r, echo=F, results='asis'}

cat(
  as.character(Sys.time())," GMT, ",
  Sys.timezone(location = TRUE),
  sep = ""
)
```


Some new stuff:
Look at how average prices change at the threshold around the first half second half change. Begin by building an indicator for what variable is changing (rp, transpo, or millcost) and only analyze data specific to those questions, otherwise you're mixing a lot of effects together.

Question 1, what parameters are changing in these different periods:
Answer: see data table below, I've figured out which paramters change in certain periods.
```{r, echo=F}

PeriodChangesFirst<-subset(sessDat, player.subperiod_number > 0 & player.subperiod_number<21&period_half=="First Half")%>% 
  group_by(player.period_number, session.code) %>% 
  summarise(
    TranspoMean = mean(player.transport_cost),
    mcMean=mean(player.mc),
    rpMean=mean(player.rp)
  )
PeriodChangesSecond<-subset(sessDat, player.subperiod_number > 0 & player.subperiod_number<21&period_half=="Second Half")%>% 
  group_by(player.period_number, session.code) %>% 
  summarise(
    TranspoMean = mean(player.transport_cost),
    mcMean=mean(player.mc),
    rpMean=mean(player.rp)
  )

PeriodChanges<-left_join(PeriodChangesFirst,PeriodChangesSecond,by = c("player.period_number", "session.code"))

PeriodChanges<-PeriodChanges%>% 
  mutate(
    TranspoChange = log(TranspoMean.y)-log(TranspoMean.x),
    mcChange=log(mcMean.y)-log(mcMean.x),
    rpChange=log(rpMean.y)-log(rpMean.x)
  )

PeriodChanges<-PeriodChanges%>% 
  mutate(
    TranspoChangeOnly = ifelse(TranspoChange != 0 & mcChange == 0&rpChange==0, TranspoChange, NA),
    mcChangeOnly = ifelse(mcChange != 0 & TranspoChange == 0&rpChange==0, mcChange, NA),
     rpChangeOnly = ifelse(rpChange != 0 & TranspoChange == 0&mcChange==0, rpChange, NA)
  )


sessDat<- left_join(sessDat,PeriodChanges[,c("player.period_number","session.code","TranspoChangeOnly","mcChangeOnly","rpChangeOnly")],by=c("player.period_number", "session.code"))


```

Want to do a regression on periods where only transport costs changed and use period fixed effects to strip out the level effects of the other parameters.

```{r, echo=F}

TranspoReg<-subset(sessDat, player.subperiod_number > 0 & player.subperiod_number<21&TranspoChangeOnly!="NA")

reg_transpo = lm(
  log(player.price) ~ factor(group_size) + log(player.transport_cost) + factor(group_size):log(player.transport_cost)+factor(player.period_number) +factor(session.code)-1,
  data = TranspoReg %>% mutate(player.price = player.price + 0.01)
)

summary(reg_transpo)

```

These results suggest that negative (insignificant) relationship between transport costs and prices in 2 player game, and positive, significant, relationship in the 4p game. These are the same results we had in the pilot study more or less. 


Want to make an event study plot transpo cost changes from first to second half. Need to select periods where only transpo costs are changing and other parameters are common. Going to look at extremes (select data that has transpo cost of 0.1 in first half then 0.6 in second half with mc=0.05 and rp=1, then also collect data that has transpo costs go from 0.6 to 0.1)

```{r, echo=F}

TranspoEvent<-subset(TranspoReg, player.mc == 0.05 & player.rp==1 &abs(TranspoChangeOnly)>1.7)

TranspoEventFHUp2p<-subset(TranspoEvent, period_half == "First Half" & player.transport_cost==0.1&group_size==2)
TranspoEventFHDown2p<-subset(TranspoEvent, period_half == "First Half" & player.transport_cost==0.6&group_size==2)
TranspoEventSHUp2p<-subset(TranspoEvent, period_half == "Second Half" & player.transport_cost==0.6&group_size==2)
TranspoEventSHDown2p<-subset(TranspoEvent, period_half == "Second Half" & player.transport_cost==0.1&group_size==2)

TranspoEventFHUp4p<-subset(TranspoEvent, period_half == "First Half" & player.transport_cost==0.1&group_size==4)
TranspoEventFHDown4p<-subset(TranspoEvent, period_half == "First Half" & player.transport_cost==0.6&group_size==4)
TranspoEventSHUp4p<-subset(TranspoEvent, period_half == "Second Half" & player.transport_cost==0.6&group_size==4)
TranspoEventSHDown4p<-subset(TranspoEvent, period_half == "Second Half" & player.transport_cost==0.1&group_size==4)

 
    
TrEvent4p= ggplot()+
  geom_smooth(data=TranspoEventFHUp4p, aes(y = player.price,x = player.subperiod_number),method = "lm",color='green')+
  geom_smooth(data=TranspoEventSHUp4p,aes(y = player.price,x = player.subperiod_number),method = "lm",color='green')+
  geom_jitter(data=TranspoEventFHUp4p,
    aes(y = player.price,x = player.subperiod_number),
    width = 0.07,
    alpha = .1)+ 
    geom_jitter(data=TranspoEventSHUp4p,
    aes(y = player.price,x = player.subperiod_number),
    width = 0.07,
    alpha = .1)+   
  geom_smooth(data=TranspoEventFHDown4p, aes(y = player.price,x = player.subperiod_number),method = "lm",color='red')+
  geom_smooth(data=TranspoEventSHDown4p,aes(y = player.price,x = player.subperiod_number),method = "lm",color='red')+
  geom_jitter(data=TranspoEventFHDown4p,
    aes(y = player.price,x = player.subperiod_number),
    width = 0.07,
    alpha = .1)+ 
    geom_jitter(data=TranspoEventSHDown4p,
    aes(y = player.price,x = player.subperiod_number),
    width = 0.07,
    alpha = .1)+
  theme_bw() +
  labs(
    x = "Superiod",
    y = "Price"
  )
TrEvent4p


TrEvent2p= ggplot()+
  geom_smooth(data=TranspoEventFHUp2p, aes(y = player.price,x = player.subperiod_number),method = "lm",color='green')+
  geom_smooth(data=TranspoEventSHUp2p,aes(y = player.price,x = player.subperiod_number),method = "lm",color='green')+
  geom_jitter(data=TranspoEventFHUp2p,
    aes(y = player.price,x = player.subperiod_number),
    width = 0.07,
    alpha = .1)+ 
    geom_jitter(data=TranspoEventSHUp2p,
    aes(y = player.price,x = player.subperiod_number),
    width = 0.07,
    alpha = .1)+
  geom_smooth(data=TranspoEventFHDown2p, aes(y = player.price,x = player.subperiod_number),method = "lm",color='red')+
  geom_smooth(data=TranspoEventSHDown2p,aes(y = player.price,x = player.subperiod_number),method = "lm",color='red')+
  geom_jitter(data=TranspoEventFHDown2p,
    aes(y = player.price,x = player.subperiod_number),
    width = 0.07,
    alpha = .1)+ 
    geom_jitter(data=TranspoEventSHDown2p,
    aes(y = player.price,x = player.subperiod_number),
    width = 0.07,
    alpha = .1)+
  theme_bw() +
  labs(
    x = "Superiod",
    y = "Price"
  )
TrEvent2p



```

Look at RP regression
```{r, echo=F}

RPReg<-subset(sessDat, player.subperiod_number > 0 & player.subperiod_number<21&rpChangeOnly!="NA")


reg_rp = lm(
  log(player.price) ~ factor(group_size) + log(player.rp) + factor(group_size):log(player.rp)+factor(player.period_number) +factor(session.code)-1,
  data = RPReg %>% mutate(player.price = player.price + 0.01)
)

summary(reg_rp)
```

Results seem to suggest that higher reserve prices (demand) increase prices in the 2p version of the game (significant at 5%). However, combining coefficients for 2p and 4p=+0.15960-0.14978= pretty much no effect for the 4 player group. This is makes sense intuitively. The rp is the upper boundary and in the 4p game, competition takes them away from that boundary and, as a result, makes it inconsequential.

Next look at cost regression:
```{r, echo=F}

mcReg<-subset(sessDat, player.subperiod_number > 0 & player.subperiod_number<21&mcChangeOnly!="NA")


reg_mc = lm(
  log(player.price) ~ factor(group_size) + log(player.mc) + factor(group_size):log(player.mc)+factor(player.period_number) +factor(session.code)-1,
  data = mcReg %>% mutate(player.price = player.price + 0.01)
)

summary(reg_mc)
```

Again, some nice results here. Costs (the bottom boundary) seem to matter, as costs increase, prices increase. The effect is stronger for 4p, which is intuitive. 4p games are closer to the bottom threshold, so when costs jump that will impact them more than the 2p games where they are pricing at much higher levels.


Look at everything together (prices)
```{r, echo=F}

AllReg<-subset(sessDat, player.subperiod_number > 0 & player.subperiod_number<21)


reg_all = lm(
  log(player.price) ~ factor(group_size) + log(player.mc)+log(player.rp) +log(player.transport_cost) + factor(group_size):log(player.transport_cost)+ factor(group_size):log(player.rp)+factor(group_size):log(player.mc)+factor(player.period_number) +factor(session.code)-1,
  data = AllReg %>% mutate(player.price = player.price + 0.01)
)

summary(reg_all)
```
Look at everything together (markups)
```{r, echo=F}

sessDat<-sessDat%>% 
  mutate(
    Markup = (player.price-player.mc)/player.mc
  )

AllReg2<-subset(sessDat, player.subperiod_number > 0 & player.subperiod_number<21)


reg_all2 = lm(
  Markup ~ factor(group_size) + log(player.mc)+log(player.rp) +log(player.transport_cost) + factor(group_size):log(player.transport_cost)+ factor(group_size):log(player.rp)+factor(group_size):log(player.mc)+factor(player.period_number) +factor(session.code)-1,
  data = AllReg2 %>% mutate(player.price = player.price + 0.01)
)

summary(reg_all2)
```

Look at average (markups)
```{r, echo=F}

reg_all3 = lm(
  Markup ~ factor(group_size) ,
  data = AllReg2 %>% mutate(player.price = player.price + 0.01)
)

summary(reg_all3)
```

AllReg<-subset(sessDat, player.subperiod_number > 0 & player.subperiod_number<21)


reg_all = lm(
  log(player.price) ~ factor(group_size) + log(player.mc)+log(player.rp) +log(player.transport_cost) + factor(group_size):log(player.transport_cost)+ factor(group_size):log(player.rp)+factor(group_size):log(player.mc)+factor(player.period_number) +factor(session.code)-1,
  data = AllReg %>% mutate(player.price = player.price + 0.01)
)

summary(reg_all)
```
Look at how well theory describes prices
```{r, echo=F}

sessDat<-sessDat%>% 
  mutate(
    PricePred1 = player.mc+player.transport_cost/group_size,
    PricePred2=player.rp-player.transport_cost/(2*group_size)
  )

sessDat<-sessDat%>% 
  mutate(
    PricePred1Err = player.price-PricePred1,
    PricePred2Err=player.price-PricePred2,
    PredDiff=PricePred2-PricePred1
  )

sessDat<-sessDat%>% 
  mutate(
   PercentError1=PricePred1Err/PredDiff
  )

PredReg<-subset(sessDat, player.subperiod_number > 0 & player.subperiod_number<21)

SumDat<-PredReg%>% 
 group_by(group_size) %>%
  dplyr::summarise(
  MeanError1=mean(PricePred1Err),
  MeanError2=mean(PricePred2Err),
  MeanError1Share = mean(PercentError1)
  )


PredReg2p<-subset(sessDat, player.subperiod_number > 0 & player.subperiod_number<21&group_size==2)

reg_Pred2p1 = lm(
  log(player.price) ~ log(PricePred1),
  data = PredReg2p %>% mutate(player.price = player.price + 0.01)
)

summary(reg_Pred2p1)

reg_Pred2p2 = lm(
  log(player.price) ~ log(PricePred2),
  data = PredReg2p %>% mutate(player.price = player.price + 0.01)
)

summary(reg_Pred2p2)

```


